% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

%% \documentclass[letterpaper,MMMMyyyy,nonstopmode]{simpleresumecv_stacked}
\documentclass[MMMMyyyy,nonstopmode]{simpleresumecv_stacked}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Edward E Griebel Jr.}
\newcommand{\CVTitle}{Ed Griebel CV}
\newcommand{\CVNote}{Resume created {\today} in \LaTeX. See it at \href{https://github.com/edgriebel/resume-cv}{\underline{github.com/edgriebel}}}
%% \newcommand{\CVNote}{Resume created in \LaTeX, check it out at \href{https://github.com/edgriebel/resume-cv}{\underline{github.com/edgriebel}}}
\newcommand{\CVWebpage}{https://www.edgriebel.com/}
\newcommand{\CVWebpageDisp}{www.edgriebel.com}

\newcommand{\tech}[1]{\Gap\textrm{Technologies:} #1}
% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}
\newcommand{\comment}[1]{\ignorespaces} %% https://tex.stackexchange.com/a/276698/143811

\newif\ifLOCATION
\newif\ifLONG
\newif\ifNOTSELECTED


\LOCATIONfalse
\LONGfalse
\NOTSELECTEDfalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%% Use Sans font
%% Default Sans font looks not too sharp, Company name in Serif font
%%\renewcommand\familydefault{\sfdefault}

%% \UseSecondaryFont %% <-- Doesn't work, doesn't switch font

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
%%
%% REPLACE WITH ADDRESS
%%
%% \textit{<my address>}
\par 
\href{mailto:edgriebel@gmail.com}
{edgriebel@gmail.com}
%%
%% REPLACE WITH CELLPHONE 
%%
$|$ %% \,\SubBulletSymbol\, 
585-705-1093
%% \,\SubBulletSymbol\,
%% \href{\CVWebpage}
%% {\url{\CVWebpageDisp}}
$|$ %% \,\SubBulletSymbol\,
\href{https://github.com/edgriebel}{github.com/edgriebel}
$|$ %% \,\SubBulletSymbol\, 
\href{https://www.linkedin.com/in/edgriebel}{linkedin.com/in/edgriebel}
\end{SubTitle}

\begin{Body}

%% \Section{Summary}{Summary}{PDF:Summary}
\item
%% ORIG

%% 2021 LinkedIn Language-Agnostic Full Stack Developer with over 20 years of success creating software solutions.
%% 2021 LinkedIn Wide breadth of experience in multiple industries, languages, tools, and third-party applications demonstrates success.
%% 2021 LinkedIn Excited to create code to deliver high quality systems that support business growth.

%% ORIG I am a full stack developer with over 20 years of consistent achievement solving diverse business problems.
%% ORIG My wide breadth of experience in multiple industries, languages, and tools demonstrates success. 
%% ORIG With 7 years remote experience I am productive in remote, hybrid, and in-office positions. 

%% V1 I am passionate about writing code and working with people to deliver systems that solve business challenges.
%% V1 As a full stack developer with over 20 years of consistent achievement 
%% V1 in multiple industries with diverse languages and tools.
%% V1 With 7 years remote experience I am productive in remote, hybrid, and in-office positions. 

%% -- ChatGPT
%% An accomplished full stack developer with consistent successes across multiple industries. 
%% Deeply passionate about collaborating with others to design and deliver innovative systems that address complex business challenges. 
\begin{center}
Staff Software Engineer with consistent success in building systems, mentoring, and making teams more productive.
Adept at partnering with people and teams to solve complex business challenges.

%% \BigGap
%% Core competencies:
%% Agile Leadership $|$ Cross-Functional Collaboration $|$ \comment{System Design $|$ } \comment{Linux $|$} Mentoring $|$ Python $|$ Java $|$ \comment{CI/CD Automation $|$ } SQL 
\end{center}
%% \Gap
%% With 7 years of remote experience I excel in working effectively in remote, hybrid, and onsite environments.
%% -- ChatGPT


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Professional Work Experience}
{Professional Work Experience}
{PDF:ProfessionalWorkExperience}

\Entry
\textbf{Lead Software and Solution Engineer}, Paychex (via Solu Technology Partners)
\hfill
\DatestampYM{2024}{09} -- Present

\Gap
\begin{Detail}
%% Technical lead for development teams, focusing on Artificial Intelligence and Java initiatives.
Leading an Agile team of SWEs and SDETs to deliver functionality for a large monolith and microservice-based payroll and HR benefits processing system.
\Gap
\BulletItem
Delivered feature to recapture \$700,000 annually in payments to terminated workers, including partnering with outside vendor across multiple release phases.
\BulletItem
Created tooling and process to validate annual billings for 600,000 clients during migration to a microservice.
\end{Detail}

\tech{Python $|$ Java $|$ Azure Cloud $|$ Oracle SQL $|$ Splunk}

\BigGap

\Entry
\textbf{Staff Software Engineer (SRE)}, Netskope
\hfill
%% \DatestampY{2023} -- \DatestampY{2024}
\DatestampYM{2023}{08} -- \DatestampYM{2024}{09}

\Gap
\begin{Detail}

Led a team of Site Reliability Engineers to support Netskope's data-loss prevention product. 
%% by aligning deliverables with partner roadmaps, including hands-on engineering and participating in on call rotations.

\Gap

\BulletItem
Partnered with dev teams to migrate Kubernetes deployments (private cloud and FedRAMP) to Spinnaker CI/CD.

%% \BulletItem
%% Capacity tool...

\BulletItem
Automated manual process to calculate data center cost savings using Python and Jenkins. 
97\% reduction in data gathering and analysis time (eight hours to 15 minutes) and reduced data center spend by \$35,000 in the first month.

%% \BulletItem
%% Participate in and supervise L1 and L2 24x7 on-call rotations during multi-year Kubernetes transformation.

\BulletItem
Implemented improvements in on-call and change management procedures to improve productivity and stability.

%% 20250501
%% \BulletItem
%% Mentored and leveled up team members and ensured that work was supportable and of sufficient quality.

%% \BulletItem
%% Implement utility to predict database capacity requirements based on existing customer metrics.

\end{Detail}

\tech{Python $|$ Kubernetes $|$ Grafana $|$ Prometheus $|$ Spinnaker $|$ Jenkins}

\BigGap

\iffalse %% Move to Education
\Entry
\textbf{Adjunct Professor}, Rochester Institute of Technology \textit{(Part-Time)}
\hfill
%% \DatestampYM{2017}{08} --
\DatestampY{2017} --
Present

%%\Gap
%%\BulletItem
\ifLOCATION
\hfill 
Rochester, New York
\fi

\Gap
\begin{Detail}
Lecturer for courses in Java, SQL/DBMS, Python/shell scripting, and commercial software engineering practices.
\end{Detail}

\BigGap
\fi

\Entry
\textbf{Production Engineer}, Meta
\hfill
\DatestampYM{2021}{08} -- \DatestampYM{2023}{07}

%%\Gap
%%\BulletItem

\Gap
\begin{Detail}
Member of Enterprise Provisioning team that automated creation of thousands of physical and virtual machines,
and Ad Serving team that dynamically allocated capacity to Machine Learning models for Facebook and Instagram ads.

\Gap

\BulletItem
%% Automated firmware updates for multiple hardware vendors across 10,000+ physical servers, eliminating ad-hoc processes and saving a week of effort for each team supporting a cluster.
	%% Automated firmware updates for multiple hardware vendors across 10,000+ physical servers. Eliminating ad-hoc updates saved a week of effort per upgrade per cluster.
	Automated firmware updates for multiple hardware vendors across 10,000+ physical servers. Eliminating ad-hoc updates across 25 clusters saved nearly a week of effort every quarter for each cluster.
\BulletItem
	%% Reduced on-call load from 20 to five hours per week by improving documentation, implementing intake processes, and automating the detection/troubleshooting of errors. 
	Reduced on-call load by 80\%, down to a half-day per week, by improving documentation, implementing intake processes, and automating error detection and troubleshooting.
\BulletItem
	Supported and enhanced systems to create/update bare metal and virtual servers using Python, Terraform, and Chef.
\BulletItem
	Led project to centralize configuration changes to ML/AI models in Meta’s ad delivery stack so AI Engineers could focus on model tuning while avoiding unintended problems or outages.

\iffalse 	%% Old version
%% Production Engineering was created at Facebook to work with engineering teams and partners to champion the Reliability, Scalability, Performance, and Security posture of production services. PEs are hybrid software and systems engineers; they are the glue holding things together, whether that’s infrastructure and software or teams and processes.

At Meta, a Production Engineer is a hybrid of Software Engineer, Site Reliability Engineer, and Systems Engineer roles
who create reliable, scalable, performant, and secure services for billions of users.

\Gap

My most recent team, Ads Serving and Delivery, automated the dynamic allocation of Machine Learning models to compute servers for all ads displayed in Facebook and Instagram.

\BulletItem
%% Lead project to implement centralized configuration changes to AI models in Facebook ad delivery stack. Effort involved identifying problematic areas and user education while ensuring these changes resulted in zero downtime or other negative impacts to ads serving stack.
Led project to centralize configuration changes to ML/AI models in Meta's ad delivery stack, allowing users to safely make changes without causing unintended problems or outages.

\Gap
My prior team created systems to automate creating thousands of new physical and virtual machines by simply editing files. 
%% using infrastructure-as-code.
\BulletItem
Created system to automate firmware updates for multiple hardware vendors across 10,000+ physical servers. 
This system eliminated creating ad-hoc scripts or manually updating servers, saving days or even weeks of effort for each team supporting a cluster of servers.

\BulletItem
Improved oncall and user experience by creating internal documentation, processes, and applications to detect and perform initial troubleshooting of common errors.
These changes reduced oncall shift impact by 60\% to under 5 hours per week.
%% Necessary changes determined by analyzing common user questions, recurring support issues, and experience during outages. 

%% \BulletItem Mentored junior and senior developers in technical and professional skill development.

%% \BulletItem
%% My team builds tools for full lifecycle automation of tens to thousands of physical servers or virtual machines by just editing a file.
%% \BulletItem
%% Selected projects: adding reliability and performance metrics including reporting to existing services; automating firmware updates across multiple hardware vendors.
\fi 		%% iffalse

\tech{Python $|$ Rust $|$ SQL $|$ Terraform $|$ Chef}

\end{Detail}

\BigGap

\Entry
\textbf{Lead Software Engineer}, Marqeta
\hfill
%% \DatestampYM{2020}{05} -- \DatestampYM{2021}{07}
\DatestampY{2020} -- \DatestampY{2021}

\ifLOCATION
\hfill
Rochester, New York
\fi
\Gap
\begin{Detail}
%% Technical lead for credit card processing including accounting ledgers and inbound transaction APIs.
%% Technical lead for credit card processing including accounting ledgers and inbound transaction APIs for new white-label credit card product.
Technical lead for new white-label credit card product including transactional ledgers and inbound transaction APIs.

\iffalse
\Gap

\BulletItem
Worked closely with developers, product owners, and operations to create a new white-label credit card product. 
\fi

%% \BulletItem
%% Established/enhanced processes and procedures for product development and support.
%% \BulletItem Mentored engineers with designs and general software engineering practices.

\tech{Java $|$ MySQL $|$ Spring Boot $|$ Docker}

\end{Detail}

\iffalse %% Hide Logical Operations
\BigGap

\Entry
\textbf{Consultant} - Logical Operations \textit{(Part-Time)}
\hfill
\DatestampY{2020} - \DatestampY{2022}

%%\Gap
%%\BulletItem
\ifLOCATION
\hfill 
Rochester, New York
\fi

\begin{Detail}
\BulletItem
Created teaching materials and subject matter expert for new courses in Machine Learning, Artificial Intelligence, and Data Science.
\end{Detail}
\fi %% Hide Logical Operations

\BigGap

\Entry
\textbf{Principal Software Engineer}, Catalant Technologies
\hfill
%% \DatestampYM{2019}{06} -- \DatestampYM{2020}{03}
\DatestampY{2019} -- \DatestampY{2020}

\ifLOCATION
\hfill
Rochester, New York
\fi

\Gap

\begin{Detail}
%% Built consensus around and implemented processes and procedures for primary SaaS product to improve supportability and developer productivity.

%% \Gap
%% \BulletItem
%% Researched issues with performance and stability issues and implemented short- and long-term projects to address them.
Researched and created plans to tackle core performance and stability issues, and fostered satellite office's culture.

%% \BulletItem
%% Mentored junior developers in company's platform and industry best practices.
%% Negotiated with managers, product owners, and CTO for resources and prioritization.
%% Determined and created immediate and 1-year plans to address performance issues impacting product stability and scalability.
%% \BulletItem
%% Negotiated with managers, product owners, and CTO for resources and prioritization.

\tech{Python $|$ Flask $|$ JavaScript $|$ Bootstrap $|$ MySQL $|$ Docker $|$ Elasticsearch}

\end{Detail}

\BigGap
%% \clearpage

%% ===========================================
%% ===========================================
%% =============     PAGE 2   ================
%% ===========================================
%% ===========================================

\Entry
\textbf{Senior Middleware Architect}, Paychex
\hfill
\DatestampY{2013} -- \DatestampY{2019}
%% \DatestampY{2013} -- \DatestampY{2019} and \DatestampY{2005} -- \DatestampY{2010}

\ifLOCATION
\hfill
Rochester, New York
\fi

\Gap
\begin{Detail}
\iffalse
At Paychex I worked with multiple cross-functional teams to build: an inventory system to track hosts, JVMs, and databases; machine learning systems in Python to efficiently rebalance databases and predict system utilization; custom Chaos Monkey ro randomly terminate process to find configuration weaknesses; and implemented AppDynamics on over 20,000 JVMs.
\fi

\iftrue
\BulletItem
Created system to rebalance 24,000 databases among 200 Azure servers with ML and statistical techniques.

%% \BulletItem Built internal inventory system with web and REST APIs providing a single source of truth for virtualized and physical hosts, JVMs, CLRs, databases, and middleware. 
%% Relationships sourced from external management systems including AppDynamics, Puppet, ServiceNow, and Oracle.

\BulletItem
Replaced a bespoke inventory system with AppDynamics to track metrics across 20,000 Java JVMs, saving 4 FTEs.

%% 20250501
%% \BulletItem
%% Created custom Chaos Monkey to regularly terminate middleware and Java processes randomly. 
%% in Production and Dev environments.
%% 20250501
%% \BulletItem
%% Built single source of truth inventory system using relationships from Puppet, ServiceNow, and Oracle.

\tech{Java $|$ JavaScript $|$ Python $|$ Scikit-Learn $|$ \comment{TensorFlow $|$} SQL $|$ AppDynamics $|$ Machine Learning}
\fi

\end{Detail}

\BigGap

\Section
{Additional Selected Experience}
{Additional Selected Experience}
{PDF:Additional Selected Experience}

\Entry
\textbf{Adjunct Professor}, Rochester Institute of Technology
\BulletItem 
Lecturer for courses in Java, SQL/DBMS, Python/shell scripting, and commercial software engineering practices.

\Entry
\textbf{Consultant and Subject Matter Expert}, Logical Operations %% \textit{(Part-Time)}
\hfill
%% \DatestampY{2020} - \DatestampY{2022}
\BulletItem
Created and advised on teaching materials for Machine Learning, Artificial Intelligence, and Data Science courses.

%% \Entry
%% \textbf{Lead Software Engineer}, Axeda/PTC
%% \hfill 
%% \DatestampYM{2010}{06} --  \DatestampYM{2013}{06}
%% \DatestampY{2010} --  \DatestampY{2013}

%%\Gap
%%\BulletItem
%% Senior Software Engineer
\ifLOCATION
\hfill
Rochester, New York
\fi

%% \begin{Detail}
%% \BulletItem
%% Fullstack Java/Oracle/Groovy/ActiveMQ JMS developer for IoT system. 
%% \BulletItem
%% NOTSELECTED Owned the integration, performance tuning, and upgrade of Cognos Business Intelligence modules.
%% \BulletItem

%% \Gap
%% Technologies: Java, JavaScript, Oracle PL/SQL, Hudson/Jenkins, Cognos, Business Intelligence
%% \end{Detail}

\ifNOTSELECTED
\Entry
\textbf{Lead Software Engineer, Paychex}
\hfill

\begin{Detail}
Led team of 6 to create three public-facing fullstack applications in Java and JavaScript.
\end{Detail}

\ifLONG
%% \BigGap
%% \textbf{******** LONG FORM TEST **********}

\Entry
\href{http://www.paychex.com/}
{\textbf{Paychex}}
\hfill 
%%\DatestampYM{2005}{03} --  \DatestampYM{2010}{06}
\DatestampY{2005} -- \DatestampY{2010}

%%\Gap
%%\BulletItem
Lead Developer
\ifLOCATION
\hfill
Rochester, New York
\fi

\begin{Detail}
%% \BulletItem
Led team of 6 to create Java/JavaScript front end and webapp for an existing internal fat client, and upgraded 2 existing web applications to contemporary standards. 

Used Hudson to create a CI/CD pipeline for Dev and QA deployments.

%% \BulletItem
%% Mentored new developers and delivered technical training.
%% 2021-05-02 TMI
\iffalse
\BulletItem
Member of architecture team to research and set five-year strategy for web application strategy.
\fi

\tech{Java, JavaScript, JSP, Struts, WebLogic, Oracle PL/SQL, Hudson/Jenkins}
\end{Detail}
\fi %% NOTSELECTED

%% Short \BigGap
\Entry
\textbf{Senior Software Engineer}, Frontier Communications
\hfill 
%% \DatestampYM{2001}{11} --  \DatestampYM{2005}{03}
\DatestampY{2001} -- \DatestampY{2005}

%%\Gap
%%\BulletItem
Senior Software Developer
\ifLOCATION
\hfill
Rochester, New York
\fi

\begin{Detail}
%% \Item
Created applications in Java to build DSL circuits and track sales commissions.

%% Automated generation of \comment{20} Excel spreadsheets from Hyperion EssBase saving 2 FTEs/\$200,000 annually.

%% \Gap
%% Technologies: Java, JSP, Struts, Oracle PL/SQL, Continuous Integration, JUnit, Excel VBA, EssBase Data Warehouse, Ant
\end{Detail}

%% SHORT \BigGap
\Entry
\textbf{Senior Software Engineer}, Global Crossing/Level3
\hfill 
%% \DatestampYM{1999}{03} --  \DatestampYM{2001}{11}
\DatestampY{1999} -- \DatestampY{2001}

%%\Gap
%%\BulletItem
Senior/Lead Developer
\ifLOCATION
\hfill
Rochester, New York
\fi

\begin{Detail}
%% \Item
Lead multi-site teams to create telecom applications in Java.
%%Lead for multi-site team creating Java application to reconcile network and order entry inventory and Perl CGI application to automate creating circuits on ATM and Frame Relay networks.

%% \Gap
%% Technologies: Perl, CGI, Java, Sybase, Solaris, Ant
\end{Detail}

%% SHORT \BigGap
\Gap
\Entry
\textbf{Senior Software Engineer}, JP Morgan Chase
\hfill 
%% \DatestampYM{1995}{06} -- \DatestampYM{1999}{02}
\DatestampY{1995} - \DatestampY{1999}

%%\Gap
%%\BulletItem
Lead Developer
\ifLOCATION
\hfill
New York, New York
\fi

\begin{Detail}
%% \Item
Created trading systems and tactical applications for equity derivatives and HFT trading desks in C++ and Excel.

%% Tech from 20 years ago would probably be considered not relevant
%% \Gap
%% Technologies: C, C++, Sybase, Excel VBA, ClearCase
\end{Detail}

%% \iffalse   %%% Hide this old job ??
%% SHORT \BigGap
\Entry
\textbf{Software Engineer}, BlackRock Financial Management
\hfill 
%% \DatestampYM{1993}{03} --  \DatestampYM{1995}{06}
\DatestampY{1993} --  \DatestampY{1995}

%%\Gap
%%\BulletItem
Software Developer
\ifLOCATION
\hfill
New York, New York
\fi

\begin{Detail}
%% \Item
Developed systems for MBS mortgage, Treasury, and Repo trading desks in C and C++.
%%\Gap
%%Technologies: C, C++, Sybase, tcl, ksh, Motif, X11
\end{Detail}
%% \fi

\iffalse
\BigGap
\Entry
\textbf{Prophet 21, Inc.}
\hfill 
Yardley, Pennsylvania

%%\Gap
%%\BulletItem
Associate Developer
\hfill
\DatestampYM{1992}{06} --  \DatestampYM{1993}{03}

\begin{Detail}
\BulletItem
Wrote and maintained features for point-of-sale systems targeted to retailers and wholesalers

\Gap
Technologies: Sybase, ksh
\end{Detail}
\fi

\else
%% \BigGap
%% \textbf{******** SHORT FORM TEST **********}

\iffalse %% merge Payx sections
\BigGap
\Entry
\href{http://www.paychex.com/}
{\textbf{Paychex}}

\begin{Detail}
%% \BulletItem
	Led team of 5 to create three public-facing fullstack Java/JavaScript applications.

	Created CI/CD deployment pipelines with Hudson.
	%% Mentored new developers and delivered technical training.
\end{Detail}
\fi %% merge Payx sections

%% \Entry
%% \textbf{Senior Software Engineer}, Frontier Communications

\ifNOTSELECTED
\begin{Detail}
%% \BulletItem
Created applications to build DSL circuits and track sales commissions in Java and SQL.
%%Automated generation of Excel spreadsheets from Hyperion EssBase saving 2 FTEs annually.
\end{Detail}
\fi %% NOTSELECTED

\ifNOTSELECTED
\Gap
\Entry
\textbf{Senior Software Engineer}, Global Crossing/Level3

\begin{Detail}
%% \BulletItem
Led multi-site teams to create telecom applications in Java and SQL.
\end{Detail}
\fi %% NOTSELECTED

%% \Entry
%% \textbf{Senior Software Engineer}, JP Morgan Chase
\ifNOTSELECTED
\begin{Detail}
%% \BulletItem
Created trading systems for equity derivatives and HFT trading desks in C, C++, and Excel.
\end{Detail}
\fi %% NOTSELECTED

%% \Entry
%% \textbf{Software Engineer}, BlackRock Financial Management
\ifNOTSELECTED
\begin{Detail}
%% \BulletItem
Developed systems for MBS mortgage, Treasury, and Repo trading desks in C and C++.
%%\Gap
%%Technologies: C, C++, Sybase, tcl, ksh, Motif, X11
\end{Detail}
\fi %% NOTSELECTED
\fi %% xxx
%
%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\textbf{Master of Science in Computer Science} -
Georgia Institute of Technology, 2023 %% (GPA: 3.9/4.0)
%% \hfill 2023

\ifNOTSELECTED %% No detail...
\BulletItem
Coursework: Compiler Optimization, CPU Architecture, LLVM Software Analysis, Applied ML and AI
\fi %% No detail....

\iftrue %% SKIP Undergrad?
%% \Gap

\Entry
\textbf{Bachelor of Science in Computer Science and Engineering} - 
Bucknell University
\ifLOCATION
\hfill Lewisburg, Pennsylvania
\fi

%%\Gap
%%\BulletItem
\iffalse
\hfill
\DatestampYM{1988}{09} --
\DatestampYM{1992}{06}
\fi
\iffalse %% Detail for undergrad?
\begin{Detail}
\BulletItem
Senior design project creating reference implementation of DHCP protocol for RFCs 1531 and 1534
%%\BulletItem
%%Summer research internship in digital image processing
\BulletItem
Concentrations in Digital Electronics and Geology

%% Technologies: Computer Science, C, VAX assembly, DHCP, TCP-IP, Digital Electronics
\end{Detail}
\fi %% Detail for undergrad
\fi %% SKIP Undergrad

%%%%%%%%%%%%
%% CERTIFICATIONS %%
%%%%%%%%%%%%
\iffalse %% SKIP CERTS
\Section
{Certifications}
{Certifications}
{PDF:Certifications}

\Entry
\href{https://www.appdynamics.com/certifications/}
{\textbf{AppDynamics Certified Implementations Professional}}
\hfill
\DatestampYM{2016}{11}
%% 2021-05-02 TMI, show cert only
\iffalse
\begin{Detail}
\begin{quote}
``An individual who attains the AppDynamics Certified Implementation Professional certification has demonstrated that he or she possesses the minimum acceptable level of knowledge and skills required to deploy AppDynamics Controllers, Agents, EUM Servers and Analytics Servers. 
This individual also has experience using AppDynamics APIs to extend and customize the AppDynamics platform.''
\end{quote}
\end{Detail}
\fi
\fi %% SKIP CERTS

%%%%%%%%%%%%%%%%%%%%%%%%%
%% Lecture EXPERIENCE  %%
%%%%%%%%%%%%%%%%%%%%%%%%%


%% 2021-05-02 DELETE entire PRESENTATION SECTION 
\newif\ifA
\newif\ifB
\newif\ifC
\Afalse
\Bfalse
\Cfalse
\ifA

\Section
{Presentations}%% and Mentoring Experience}
{Presentation}%%  and Mentoring Experience}
{PDF:Presentations}%%AndMentoringExperience}

%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse      %% INCLUDE only for cv style
%%%%%%%%%%%%%%%%%%%%%%%%%
\Entry
\textbf{Adjunct Lecturer}
\hfill
Fall 2017

Rochester Institute of Technology
\begin{Detail}
\Item
Lecturer for a class of 30 undergraduate and graduate students for the course ISTE-120, an introduction to Java course for Information Science and Technology majors.
\end{Detail}

\BigGap
\Entry
\textbf{Summer Co-Op Mentor}
\hfill
Summer 2015

Paychex, Inc.
\begin{Detail}
\Item
After interviewing a number of students, our team brought on a college student for three months. During that time I mentored them on their development tasks, our software development life cycle, version control, and working on a real-world development team. During this time I had the opportunity to give feedback on code, show how things learned in the classroom apply to corporate development, and work through actual software engineering problems.
\end{Detail}
\fi      %% INCLUDE only for cv style

\BigGap
\Entry
\textbf{Axeda Reporting -- A Guide to Service Intelligence} (Trade Conference)
\hfill
\DatestampYMD{2013}{05}{08}

Axeda Connection Conference, Axeda, Inc.
\begin{Detail}
\Item
Live presentation for Axeda customers to review and demonstrate new features added to the Cognos big data reporting product.
\ifB
\Item
From the conference program:
\begin{quote}
Service Intelligence enables your organization to apply analytics and decision-making, anytime, anywhere. See an overview of Axeda Reporting and what changes are coming in the near future. This session will include live demos of standard reports, as well creating custom reports with Report Studio.
\end{quote}
\fi
\end{Detail}

\ifC      %% INCLUDE only for cv style
\BigGap
\Entry
\textbf{Java Technical Lead and Team Lead}
\hfill
\DatestampY{2005} -- 
\DatestampY{2010}

Paychex, Inc.
\begin{Detail}
\BulletItem
As one of the technical leads for Java, developers on the extended team would come to me when they had deep technical questions about their code or odd errors that they couldn't track down. I would also have conversations with experienced developers to determine the ``best'' solution for a problem that would meet given technical or scheduling constraints.
\BulletItem
The department I was in created training exercises for new developers to introduce them to the tools and development environment. I worked with each new developer to review their answers to the Java exercises,  answer questions as they worked through them, and working through topics new to them.
\BulletItem
I gave quarterly presentations to the extended team to introduce Java technologies and internal systems. Topics included web application redesigns and base functionality, Java JSP and servlet development, and web testing techniques.
\BulletItem
As a Java team lead, I was responsible for a small team of developers. Since this was the first job after college for some, as we reviewed their code I would see opportunities to mentor them on advanced Java and JavaScript concepts and topics.
\end{Detail}
\fi      %% INCLUDE only for cv style

\fi %% DELETE entire PRESENTATION SECTION 

%%%%%%%%%%%%
%% AWARDS %%
%%%%%%%%%%%%
\iffalse %% SKIP AWARDS

\Section
{Awards}
{Awards}
{PDF:Awards}
\textbf{Paychex Paragon Award for Resiliency}
\hfill
\DatestampY{2019}
%% \DatestampYM{2019}{01}
\begin{Detail}
%% Every year, five projects are chosen across Paychex that demonstrate resiliency, exceptional delivery, operational efficiency, etc.
Our project, "Adaptive Load Balancing", was chosen for this annual award. 
It routes requests in F5 BigIP GTM and LTMs across servers and data centers based on server load, real-time statistics, and other measures to reduce outages and improve response times for services.
\end{Detail}
\BigGap

\textbf{AppDynamics Scale Award}
\hfill
%% \DatestampYM{2015}{11}
\DatestampY{2015}
%% \begin{Detail}
%% Awarded by AppDynamics to the company that was able to quickly deploy the AppDynamics tool across the most complex environment. 

Awarded for successfully deploying AppDynamics to over 20,000 JBoss, WebLogic, and Windows IIS servers across our fleet in our first year.
%% \end{Detail}
\fi %% SKIP AWARDS

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

%%%%%%%
%%% KEEP THIS SECTION???
%%%%%%%
\iffalse
\Section
{Publications}
{Publications}
{PDF:Publications}

\SubSection
{Technical Editor}
{Technical Editor}
{PDF:TechnicalEditor}

%% MLA format
\Entry
\href{https://www.amazon.com/Oracle-Certified-Associate-ProgrammerStudy/dp/1849687323}
{Reece, Richard M. \textit{Oracle Certified Associate, Java SE 7 Programmer Study Guide}, Packt Publishing, 2012}

\Gap
\Entry
\href
{https://www.amazon.com/Java-Concurrency-Cookbook-FernandezJavier/dp/1849687889}
{Gonzalez, Javier Fernandez. \textit{Java 7 Concurrency Cookbook}, Packt Publishing, 2012}
\fi

%%%%%%%%%%%%%%%%%%%%%%
%% OTHER ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%
% \Section
% {Activities}
% {Activities}
% {PDF:OtherActivities}

% \Entry
% \textbf{Leader, Boy Scouts and Cub Scouts}
% \hfill
% \DatestampY{2007} -- Present

% \Entry
% \textbf{FAA Certified Private Pilot}
%%\hfill
%%\DatestampY{2000}
\iffalse
  \Gap
  \begin{center}
    [\textit{\CVNote}]
  \end{center}
\fi
  
\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

%% \UseNoteFont%
%% \null\hfill%
%% [\textit{\CVNote}]
\end{document}

